\vspace{-1em}\thetitle

### 2009-09-22 paper.tex
...

\section*{Extended Abstract}

@@

For our experiments, we use randomly sampled traffic from six network traces.
The traces are freely available from the \caps{CRAWDAD} trace repository~\cite{Yeo06}.
Details of the traces are shown in \Table{traces}.
% These data sets represent a broad cross-section of traffic patterns over time and a reasonable variety of network types.
% Unfortunately, we could not find any freely available residential or corporate network traces that were usable for our analysis.
We randomly sampled 5000 flows from each trace for training and another 5000 flows for testing.
% Since the initial five packets are used for prediction, we consider only flows with at least five packets.
The results are shown in \Figure{accuracy}.
The left panel shows the accuracy rates of predicting packet size and inter-packet interval distributions.
Accuracy is computed by comparing the distribution of Kolmogorov-Smirnov (K-S) test p-values to an empirical ideal distribution of K-S p-values, taking the maximum deviation from the ideal as the error rate.
Three prediction techniques are employed:
prediction based on our hypothesis and model;
predicting the already observed behavior of each flow;
predicting the average behavior of the training trace.
The right-top panel shows the accuracy rate for predicting which flow will have more packets between random pairs of flows.
Choosing randomly gives 50\% accuracy, which we exceed significantly on all traces.

@@

\renewcommand{\thesection}{\textsection}
\vspace{-0.15em}
\scriptsize
\bibliographystyle{unsrt}
\bibliography{references}

>>>>

\vspace{-0.5em}
\section*{Extended Abstract}

@@

For our experiments, we use randomly sampled traffic from six network traces.
The traces are freely available from the \caps{CRAWDAD} trace repository~\cite{Yeo06}.
Details of the traces are shown in \Table{traces}.
% These data sets represent a broad cross-section of traffic patterns over time and a reasonable variety of network types.
% Unfortunately, we could not find any freely available residential or corporate network traces that were usable for our analysis.
We randomly sampled 5000 flows from each trace for training and another 5000 flows for testing.
% Since the initial five packets are used for prediction, we consider only flows with at least five packets.
The results are shown in \Figure{accuracy}.
The left panel shows the accuracy rates of predicting packet size and inter-packet interval distributions.
Accuracy is computed by comparing the distribution of Kolmogorov-Smirnov (K-S) test p-values to an empirical ideal distribution of K-S p-values, taking the maximum deviation from the ideal as the error rate.
Since no previous work attempts to either model individual flow behavior or predict flow behavior from initial observations, we compare our prediction technique to two simple and obvious approaches:
predicting the already observed behavior of each flow, and
predicting the average behavior of the training trace.
The right-top panel shows the accuracy rate for predicting which flow will have more packets between random pairs of flows.
Choosing randomly gives 50\% accuracy, which we exceed significantly on all traces.

@@

\vspace{-0.5em}
\scriptsize
\bibliographystyle{unsrt}
\bibliography{references}
